Periodograms for Multiband Astronomical Time Series

### 2015-02-03 writeup/paper.tex
add LSST results to abstract

\begin{abstract}
This paper introduces the {\it multiband periodogram}, a general extension of the standard 
Lomb-Scargle approach for detecting periodic signals in time-domain data. In addition to 
advantanges of the Lomb-Scargle method such as treatment of non-uniform sampling and
heteroscedastic errors, the multiband periodogram significantly improves period finding for randomly 
sampled multiband light curves (e.g., Pan-STARRS, DES and LSST). The light curves in 
each band are modeled as arbitrary truncated Fourier series, with the period and phase 
shared across all bands. The key aspect is the use of Tikhonov regularization which drives
most of the variability into the so-called base model common to all bands, while 
fits for individual bands describe residuals relative to the base model and typically require
lower-order Fourier series. This decrease in the required number of fit parameters is the
main reason for improved performance. We use simulated light curves 
and randomly subsampled SDSS Stripe 82 data to demonstrate the superiority of this 
method compared to other methods from the literature. The Python implementation of 
this method, along with code to fully reproduce the results reported here, is available on GitHub.
\end{abstract}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{fig09.pdf}
  \caption{
  } 
  \figlabel{LSST_sims}
\end{figure}

>>>>

\begin{abstract}
This paper introduces the {\it multiband periodogram}, a general extension of the standard 
Lomb-Scargle approach for detecting periodic signals in time-domain data. In addition to 
advantanges of the Lomb-Scargle method such as treatment of non-uniform sampling and
heteroscedastic errors, the multiband periodogram significantly improves period finding for randomly 
sampled multiband light curves (e.g., Pan-STARRS, DES and LSST). The light curves in 
each band are modeled as arbitrary truncated Fourier series, with the period and phase 
shared across all bands. The key aspect is the use of Tikhonov regularization which drives
most of the variability into the so-called base model common to all bands, while 
fits for individual bands describe residuals relative to the base model and typically require
lower-order Fourier series. This decrease in the required number of fit parameters is the
main reason for improved performance. We use simulated light curves 
and randomly subsampled SDSS Stripe 82 data to demonstrate the superiority of this 
method compared to other methods from the literature, and find that this method will be able to
efficiently determine the correct period in the majority of LSST's bright RR Lyrae stars with
as little as six months of LSST data.
The Python implementation of this method, along with code to fully reproduce the results
reported here, is available on GitHub.
\end{abstract}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{fig09.pdf}
  \caption{
    Fraction of periods correctly determined for LSST RR Lyrae as a function
    of observing time and $g$-band magnitude, for the multiband (solid lines)
    and single-band supersmoother (dashed lines) approaches.
  } 
  \figlabel{LSST_sims}
\end{figure}
